Temporality is Important for Networks of Hospital Patient Transfers

### 2025-04-09 reports/report.qmd
small content adds

The modelling of patient transfers between hospitals has historically been done by using static networks.

@@

>>>>

The modelling of patient transfers between hospitals has historically been done by using static networks. We show here that this can lead to misleading estimates of the extent of the spread of patients over time. This has implications for surveillance and control of infections that are transferred between healthcare facilities by patients, such as CPE.

@@

## Estimation of Hospital Capacity

Central to our model of the movement dynamics is the quantity $N_u$, the "size" of each hospital.
We assume that this is constant over time, which is rather dubious, since hospitals can be reconfigured, expanded, or shrunk to meet administrative and operational needs.

We make a few assumptions to reach the hospital size estimates:

1. Healthcare facilities, on average, churn a number patients the equivalent of their size within a day.
2. Some proportion of these churned individuals are readmissions to the same facility.
3. There is a minimum size of 5.

Then the size can be approximated as the number of transfers (that are not self-transfers) ...
